\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling

### 2013-03-09 jss/article.tex
change

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
        Hyung Suk Tak\\Harvard University \And
        Carl Morris\\ Harvard University}
\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Joseph Kelly\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{kelly2@fas.harvard.edu}\\
  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

>>>>

%% almost as usual
\author{Joseph Kelly\\Harvard University \And 
        Hyungsuk Tak\\Harvard University \And
        Carl Morris\\ Harvard University}
\title{\pkg{Rgbp}: Empirical Bayesian Hierarchical Modeling}

@@

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Joseph Kelly\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{kelly2@fas.harvard.edu}\\
  URL: \url{http://www.people.fas.harvard.edu/~kelly2/}\\

  Hyungsuk Tak\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{tak@fas.harvard.edu}\\

  Carl Morris\\
  Department of Statistics\\
  Harvard University\\
  1 Oxford Street, Cambridge, MA\\
  E-mail: \email{morris@fas.harvard.edu}\\
}

%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851
